%-------------------------
% Resume in Latex
% Author : Hozaifa Moustafa
% Adapted for: Hozaifa Moustafa
% Inspired by: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{lmodern}

% --- FIX: Add T1 font encoding ---
\usepackage[T1]{fontenc} 
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{5pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge\scshape Hozaifa Moustafa} \\ \vspace{4pt}
    \small 
    Alexandria, Egypt $\cdot$ +201033199960 $\cdot$ 
    \href{mailto:Hozaifa.dev@outlook.com}{\underline{Hozaifa.dev@outlook.com}} \\
    \href{https://www.linkedin.com/in/hozaifamoustafa/}{\underline{linkedin.com/in/hozaifamoustafa}} $\cdot$ 
    \href{https://github.com/HozaifaDev}{\underline{github.com/HozaifaDev}}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{Data Scientist and Data Engineer with a track record of building production-ready AI systems, automated data pipelines, and intelligent analytics platforms. Taught 400+ students industry-standard data frameworks. Led IEEE student branch from 0 to 170+ members.}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pharos University}{Alexandria, Egypt}
      {B.Sc. Computer Science \& AI, Data Science Major $\cdot$ GPA: 3.0/4.0}{Sep 2022 -- Jun 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Alshaya AI}{Remote (KSA)}
      {Operation \& Automation Engineer}{Dec 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Building automated solutions for legacy systems, serving clients across KSA, China, and global markets.}
        \resumeItem{Enhancing client experience and reducing operational overhead through intelligent workflow automation.}
      \resumeItemListEnd

    \resumeSubheading
      {Arabian Academy}{Alexandria, Egypt}
      {Data Analysis Instructor}{Sep 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Instructed 400+ graduates in industry-standard data analysis frameworks, emphasizing practical implementation and real-world data workflows.}
        \resumeItem{Enabled graduates to build automated daily, weekly, and monthly data pipelines, directly improving job placement rates and operational efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {STC TV}{Remote (KSA)}
      {Data Analytics Intern}{Aug 2024}
      \resumeItemListStart
        \resumeItem{Designed and implemented a predictive recommendation system using hybrid TF-IDF metadata modeling and custom engagement forecasting (ARIMA/SARIMA), driving a 28\% increase in content personalization metrics.}
        \resumeItem{Streamlined viewer metric definitions, resolving structural churn analysis uncertainties to optimize executive visual dashboards.}
      \resumeItemListEnd

    \resumeSubheading
      {Pharos University}{Alexandria, Egypt}
      {Volunteer Programming Instructor}{Summers 2023 -- 2025}
      \resumeItemListStart
        \resumeItem{Taught foundational programming, data structures, and OOP design to undergraduate students across three summer cohorts.}
        \resumeItem{Inspired students to independently build data projects post-course, with several securing industry roles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{UpHeal RAG System} $|$ \emph{Python, ChromaDB, Sentence Transformers, LLM Agents}}{Nov 2025 -- Jun 2026}
          \resumeItemListStart
            \resumeItem{Built a multi-agent RAG orchestration system with a Bayesian Network assessment engine to automate healthcare decision workflows. \href{https://github.com/Upheal1/Upheal-RAG-System}{\underline{github.com/Upheal1/Upheal-RAG-System}}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Media Station} $|$ \emph{Python, Scrapy, BERT, Tableau, PostgreSQL}}{Client Project}
          \resumeItemListStart
            \resumeItem{Built an automated data pipeline using asynchronous web scraping and BERT-based sentiment analysis to deliver real-time news monitoring dashboards for a media client.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Invoice Processing Pipeline} $|$ \emph{Python, Django, OpenCV, PostgreSQL}}{Client Project}
          \resumeItemListStart
            \resumeItem{Developed a document parsing and computer vision pipeline to automate invoice data extraction, ledger matching, and transactional accounting workflows.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Salary \& Manager Tracking System} $|$ \emph{Python, Pandas, SQL, Power BI}}{2025}
          \resumeItemListStart
            \resumeItem{Engineered an ETL and database normalization framework to track salary disbursements, audit managerial discrepancies, and flag anomalies via relational data logic. \href{https://github.com/HozaifaMoustafa/tracking-bad-managers-salary-payment}{\underline{github.com/HozaifaMoustafa/tracking-bad-managers-salary-payment}}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Amazon Reviews Sentiment Analysis} $|$ \emph{Deep Learning, Python}}{Oct 2024}
          \resumeItemListStart
            \resumeItem{Built a deep sequential neural model for sentiment classification of customer reviews. Presented findings at ESPC IEEE Section Egypt on marketing strategy applications.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------VOLUNTEERING & LEADERSHIP-----------
\section{Volunteering \& Leadership}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Chairman} $|$ IEEE PUA Student Branch}{May 2024 -- Dec 2025}
        \resumeItemListStart
          \resumeItem{Built the branch from 0 to 170+ students with 50+ core members across HR, Technical, and PR committees.}
          \resumeItem{Organized 5 mega events with 300+ attendees; established full operational documentation, meeting schedules, and committee reports customized for Pharos University regulations.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Founder} $|$ Pharos Foresight Magazine}{Jan 2024 -- Jun 2024}
    \resumeProjectHeading
        {\textbf{Technical Member} $|$ Google Developer Student Clubs (GDSC)}{Sep 2023 -- Jun 2024}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, R, Bash} \\
     \textbf{Data Engineering}{: ETL Pipelines, Data Modeling, PostgreSQL, Docker, Scrapy} \\
     \textbf{Data Science \& AI}{: LLM Orchestration, RAG, Agentic Architectures, ML/DL (RNN, LSTM), BERT, Tableau, Power BI} \\
     \textbf{Developer Tools}{: Git, GitHub, Excel, LaTeX}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications \& Training}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Data Analytics Specialist} $|$ Google - Digital Egypt Pioneers Initiative (DEPI)}{Apr 2024 -- Oct 2024}
    \resumeProjectHeading
        {\textbf{Quantum Computing \& Programming} $|$ QBronze138 -- QWorld}{Aug 2023}
    \resumeProjectHeading
        {\textbf{Entrepreneurship Training} $|$ ITIDA -- TIED InnovEgypt}{Sep 2023}
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{SeaPerch ROV Competition} $|$ 2nd Place}{Aug 2025}
    \resumeProjectHeading
        {\textbf{ICMTC Competition} $|$ Speech Recognition Model}{Jun 2024}
    \resumeProjectHeading
        {\textbf{ECPC} $|$ Competitive Programming}{Jun 2023}
  \resumeSubHeadingListEnd

\end{document}
